%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Recruitment Officer \\
Dynetics \\
1002 Explorer Boulevard\\
Huntsville, Alabama 35806} 


%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
%\large\bf 
Paul R Schwendenman \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
3009 Crescent Drive \\ Columbus, Ohio 43204-2524 \\ (614) 356-7807 % Your address and phone number
\end{center} 
\vfill

\signature{Paul Schwendenman} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Recruiter,} 

I am looking for a full time position at Dynetics. I meet and interviewed
with Mark Brockman during a career fair at the Ohio State University.  I am
not applying for a specific position at this time.  I would prefer to work
at the Dayton location, but given the right opportunity I am willing to
relocate out of Ohio.
 
My graduating GPA was 3.261 which is lower than the typically desired 3.5
GPA.  Ohio State as underwent a quarter to semester transition which skewed
the numbers a bit.  I graduated in three and a half years and did not have
much padding to overcome some of my lower grades.  I took challenging
classes and often far to many classes.  In retrospect, I don't think this
was the best strategy as it does not reflect my intelligence or competency
accurately.  Specifically in a few classes like DSP, I earned lower grades
by not testing well on midterm exams.  My strongest skillset is software and
coding based.  However, I have experience and interest in hardware areas. 
For example, I have worked with both FPGAs and microcontrollers. 
Consequently, I believe I am uniquely able to provide a solid mix of
hardware and software knowledge.

I am willing to travel to Huntsville or to another location for an
interview.  For any additional questions, feel free to call (614-356-7807)
or email me (schwendenman.paul@gmail.com).  Thank you for your time and
consideration.

\closing{Sincerely,}


\encl{resume, transcript} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}